Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-16 content/appendix.tex
pass halfway through proofs

\subsection*{Representation of Micro Functions}
We start by presenting the proofs to the lemmas about the representation of micro functions.

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalEq}}]
First, we need to show that for all $r\in R$ and ${m\in R\to2^T}$, if $I(r)=I'(r)$ and $U(r)=U'(r)$, then $\denote{\setpair IU}(m)(r)=\denote{\setpair{I'}{U'}}(m)(r)$. Indeed, we can see that
\begin{align*}
  \denote{\setpair IU}(m)(r)
  &=\left(\lambda m'\,.\,\lambda r'\,.\,(m'(r')\cap I(r'))\cup U(r')\right)(m)(r)\\
  &=(m(r)\cap I(r))\cup U(r)\\
  &=(m(r)\cap I'(r))\cup U'(r)\\
  &=\left(\lambda m'\,.\,\lambda r'\,.\,(m'(r')\cap I'(r'))\cup U'(r')\right)(m)(r)\\
  &=\denote{\setpair{I'}{U'}}(m)(r).
\end{align*}

@@

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalComp}}]
For all $r\in R$ and $m\in R\to2^T$,
\begin{align*}
  &\denote{\setpair IU\circ\setpair{I'}{U'}}(m)(r)\\
  &=\denote{\setpair{\lambda r'\,.\,(I(r')\cap I'(r'))\cup U(r')}
                    {\lambda r'\,.\,(I(r')\cap U'(r'))\cup U(r')}}(m)(r)\\
  &=(m(r)\cap(I(r)\cap I'(r))\cup U(r))\cup(I(r)\cap U'(r))\cup U(r)\\
  &=(m(r)\cap I'(r))\cup I(r)\cup (U'(r)\cap I(r))\cup U(r)\\
  &=(((m(r)\cap I'(r))\cup U'(r))\cap I(r))\cup U(r)\\
  &=\left(\lambda r'.(((m(r')\cap I'(r'))\cup U'(r'))\cap I(r'))\cup U(r')\right)(r)\\
  &=\left(\lambda m'.\lambda r'.(m'(r')\cap I(r'))\cup U(r')\right)
    \left(\left(\lambda m'.\lambda r'.(m'(r')\cap I'(r'))\cup U'(r')\right)  (m)\right)(r)\\
  &=\left(\denote{\setpair IU}\circ\denote{\setpair{I'}{U'}}\right)(m)(r).\qedhere
\end{align*}
\end{proof}

>>>>

\subsection*{Representation of Micro Functions}
\otodo{Repeat the lemmas here before each proof.}
We start by presenting the proofs to the lemmas about the representation of micro functions.

\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalEq}}]
    OL: Can't we just say the following?
    \begin{align*}
        \denote{\setpair {I}{U}}\\
       & = \lambda m. \lambda r. (m(r) \cap I(r))\cup U(r))\\
       & = \lambda m. \lambda r. (m(r) \cap I'(r))\cup U'(r))\\
       & = 
        \denote{\setpair {I'}{U'}}\\
    \end{align*}

First, we need to show that for all $r\in R$ and ${m\in R\to2^T}$, if $I(r)=I'(r)$ and $U(r)=U'(r)$, then $\denote{\setpair IU}(m)(r)=\denote{\setpair{I'}{U'}}(m)(r)$. Indeed, we can see that
\begin{align*}
  \denote{\setpair IU}(m)(r)
  &=\left(\lambda m'\,.\,\lambda r'\,.\,(m'(r')\cap I(r'))\cup U(r')\right)(m)(r)\\
  &=(m(r)\cap I(r))\cup U(r)\\
  &=(m(r)\cap I'(r))\cup U'(r)\\
  &=\left(\lambda m'\,.\,\lambda r'\,.\,(m'(r')\cap I'(r'))\cup U'(r')\right)(m)(r)\\
  &=\denote{\setpair{I'}{U'}}(m)(r).
\end{align*}

OL: Again, we can keep it simpler:
For the other direction:
\begin{align*}
&&
    \denote{\setpair{I}{U}} &= \denote{\setpair{I'}{U'}}\\
&\implies &
    \denote{\setpair{I}{U}}(\lambda r. \emptyset) &= \denote{\setpair{I'}{U'}}(\lambda r. \emptyset)\\
&\implies &
(\lambda m.\lambda r.(m(r)\cap I(r))\cup U(r))(\lambda r.\emptyset) &=
(\lambda m.\lambda r.(m(r)\cap I'(r))\cup U'(r))(\lambda r.\emptyset) \\
&\implies &
\lambda r.(\emptyset \cap I(r))\cup U(r) &=
\lambda r.(\emptyset \cap I'(r))\cup U'(r) \\
&\implies &
\lambda r.U(r) &=
\lambda r.U'(r) \\
&\implies &
U &=
U' \\
\end{align*}
Similarly:
\begin{align*}
&&
    \denote{\setpair{I}{U}} &= \denote{\setpair{I'}{U'}}\\
&\implies &
\denote{\setpair{I}{U}}(I) &= \denote{\setpair{I'}{U'}}(I)\\
&\implies &
(\lambda m.\lambda r.(m(r)\cap I(r))\cup U(r))(I) &=
(\lambda m.\lambda r.(m(r)\cap I'(r))\cup U'(r))(I) \\
&\implies &
\lambda r.(I(r) \cap I(r))\cup U(r) &=
\lambda r.(I(r) \cap I'(r))\cup U'(r) \\
&\implies &
\lambda r.(I(r) \cap I(r)) &=
\lambda r.(I(r) \cap I'(r)) \textrm{ since $\forall r.U(r) \subseteq I(r)$} \\
&\implies \forall r.&
I(r) &= I(r) \cap I'(r)\\
&\implies \forall r.&
I(r) &\subseteq I'(r)\\
\end{align*}
Symmetrically, we can also establish that $\forall r.I'(r) \subseteq I(r)$ by applying the functions to $I'$ instead of to $I$. Therefore, $I = I'$.

@@

\otodo{The (m)(r) does not seem necessary. Can we replace $r'$ with $r$ and $m'$ with $m$?}
\begin{proof}[\textbf{Proof of Lemma~\ref{lem:equalComp}}]
For all $r\in R$ and $m\in R\to2^T$,
\begin{align*}
  &\denote{\setpair IU\circ\setpair{I'}{U'}}(m)(r)\\
  &=\denote{\setpair{\lambda r'\,.\,(I(r')\cap I'(r'))\cup U(r')}
                    {\lambda r'\,.\,(I(r')\cap U'(r'))\cup U(r')}}(m)(r)\\
  &=(m(r)\cap(I(r)\cap I'(r))\cup U(r))\cup(I(r)\cap U'(r))\cup U(r)\\
  &=(m(r)\cap I'(r))\cup I(r)\cup (U'(r)\cap I(r))\cup U(r)\\
  &=(((m(r)\cap I'(r))\cup U'(r))\cap I(r))\cup U(r)\\
  &=\left(\lambda r'.(((m(r')\cap I'(r'))\cup U'(r'))\cap I(r'))\cup U(r')\right)(r)\\
  &=\left(\lambda m'.\lambda r'.(m'(r')\cap I(r'))\cup U(r')\right)
    \left(\left(\lambda m'.\lambda r'.(m'(r')\cap I'(r'))\cup U'(r')\right)  (m)\right)(r)\\
  &=\left(\denote{\setpair IU}\circ\denote{\setpair{I'}{U'}}\right)(m)(r).\qedhere
\end{align*}
\end{proof}
